Run the model

### 2019-05-22 scripts/model/2_run_model.Rmd
Added scripts

```{r, fig.width = 4, fig.height = 4}
(
  costs_no_trading_plot <-
    ggplot(data = DF_1_no_trading) +
    geom_line(aes(
      x = R,
      y = rel_cost,
      group = theta,
      color = theta
    ),
    size = 1
    ) +
    xlab("Portion of patch as reserve (R)") +
    ylab("Costs\n(% of case with R = 0)") +
    scale_color_viridis_c() +
    theme(
      text = element_text(size = 10),
      axis.text = element_text(size = 8)
    ) +
    startR::ggtheme_plot() +
    scale_y_continuous(labels = scales::percent) +
    guides(color = guide_colorbar(title = quo("Movement ("~theta~")"),
                                  ticks.colour = "black", frame.colour = "black")) +
    theme(legend.justification = c(0, 0.9),
          legend.position = c(0, 1)) +
    geom_abline(intercept = 0, slope = 1, size = 1, linetype = "dashed", color = "red")
)
```

@@

```{r, fig.width = 4, fig.height = 4}
(costs_with_trading_plot_long_axis <- ggplot(data = DF_1_with_trading) +
  geom_line(aes(
    x = R,
    y = rel_cost,
    group = theta,
    color = theta
  ),
  size = 1
  ) +
  xlab("Portion of patch as reserve (R)") +
  ylab("Costs (% of case with R = 0)") +
  scale_color_viridis_c() +
  startR::ggtheme_plot() +
  scale_y_continuous(labels = scales::percent, limits = c(0, 1)) +
  theme(legend.position = "None"))
```

@@

```{r}
(costs_with_trading_plot <- ggplot(data = DF_1_with_trading) +
  geom_line(aes(
    x = R,
    y = rel_cost,
    group = theta,
    color = theta
  ),
  size = 1
  ) +
  xlab("Portion of patch as reserve (R)") +
  ylab("Costs\n(% of case with R = 0)") +
  scale_color_viridis_c() +
  startR::ggtheme_plot() +
  scale_y_continuous(labels = scales::percent_format(accuracy = 0.01)) +
  theme(legend.position = "None"))
```

@@

```{r}
(delta_costs_plot <- ggplot(data = both) +
  geom_line(aes(
    x = R,
    y = rel_delta_cost,
    group = theta,
    color = theta
  ),
  size = 1
  ) +
  xlab("Portion of patch as reserve (R)") +
  ylab("Costs avoided\nby trading") +
  scale_color_viridis_c(limits = c(0, 1)) +
  theme(
    text = element_text(size = 10),
    axis.text = element_text(size = 8)
  ) +
  startR::ggtheme_plot() +
  scale_y_continuous(labels = scales::percent_format(accuracy = 0.1)) +
  theme(legend.position = "None"))
```

@@

```{r, fig.height = 3.5, fig.width = 4.5}
(allocation_cost_plot <- allocation %>%
   filter(R > 0,
          trade) %>% 
   mutate(trade = ifelse(trade, "Trading", "No Trading"),
          theta = as.character(theta)) %>% 
   group_by(trade, alpha, R, theta) %>%
   summarize(rev = sum(rev_tot)) %>%
   ungroup() %>%
   mutate(cost = (best_rev - rev) / best_rev) %>%
   ggplot(aes(x = R, y = cost, color = alpha, group = paste(alpha, theta), linetype = theta)) +
   geom_line(size = 1.5) +
   scale_y_continuous(labels = scales::percent) +
   xlab("Portion of patch as reserve (R)") +
   ylab("Costs\n(% of case with R = 0)") +
   scale_color_viridis_c() +
   scale_linetype_manual(values = c("solid", "dashed", "dotted")) +
   ggtheme_plot() +
   # facet_wrap(~trade, ncol = 1) +
   guides(color = guide_colorbar(title = quo("Allocation\nparameter ("~alpha~")"),
                                 ticks.colour = "black",
                                 frame.colour = "black"),
          linetype = guide_legend(title = quo("Movement\nparameter ("~theta~")"),
                                  override.aes = list(size = 0.5))))
```

>>>>

```{r, fig.width = 4, fig.height = 4}
(
  costs_no_trading_plot <-
    ggplot(data = DF_1_no_trading) +
    geom_line(aes(
      x = R,
      y = rel_cost,
      group = theta,
      color = theta
    ),
    size = 1
    ) +
    xlab("Portion of patch as reserve (R)") +
    ylab("Losses\n(relative to R = 0)") +
    scale_color_viridis_c() +
    theme(
      text = element_text(size = 10),
      axis.text = element_text(size = 8)
    ) +
    startR::ggtheme_plot() +
    scale_y_continuous(labels = scales::percent) +
    guides(color = guide_colorbar(title = quo("Movement ("~theta~")"),
                                  ticks.colour = "black", frame.colour = "black")) +
    theme(legend.justification = c(0, 0.9),
          legend.position = c(0, 1)) +
    geom_abline(intercept = 0, slope = 1, size = 1, linetype = "dashed", color = "red")
)
```

@@

```{r, fig.width = 4, fig.height = 4}
(costs_with_trading_plot_long_axis <- ggplot(data = DF_1_with_trading) +
  geom_line(aes(
    x = R,
    y = rel_cost,
    group = theta,
    color = theta
  ),
  size = 1
  ) +
  xlab("Portion of patch as reserve (R)") +
  ylab("Losses (relative to R = 0)") +
  scale_color_viridis_c() +
  startR::ggtheme_plot() +
  scale_y_continuous(labels = scales::percent, limits = c(0, 1)) +
  theme(legend.position = "None"))
```

@@

```{r}
(costs_with_trading_plot <- ggplot(data = DF_1_with_trading) +
  geom_line(aes(
    x = R,
    y = rel_cost,
    group = theta,
    color = theta
  ),
  size = 1
  ) +
  xlab("Portion of patch as reserve (R)") +
  ylab("Losses\n(relative to R = 0)") +
  scale_color_viridis_c() +
  startR::ggtheme_plot() +
  scale_y_continuous(labels = scales::percent_format(accuracy = 0.01)) +
  theme(legend.position = "None"))
```

@@

```{r}
(delta_costs_plot <- ggplot(data = both) +
  geom_line(aes(
    x = R,
    y = rel_delta_cost,
    group = theta,
    color = theta
  ),
  size = 1
  ) +
  xlab("Portion of patch as reserve (R)") +
  ylab("Costs avoided\nby trading") +
  scale_color_viridis_c(limits = c(0, 1)) +
  theme(
    text = element_text(size = 10),
    axis.text = element_text(size = 8)
  ) +
  startR::ggtheme_plot() +
  scale_y_continuous(labels = scales::percent_format(accuracy = 0.1),
                     limits = c(0.885, 1)) +
  theme(legend.position = "None"))
```

@@

```{r, fig.height = 3.5, fig.width = 4.5}
(allocation_cost_plot <- allocation %>%
   filter(R > 0,
          trade) %>% 
   mutate(trade = ifelse(trade, "Trading", "No Trading"),
          theta = as.character(theta)) %>% 
   group_by(trade, alpha, R, theta) %>%
   summarize(rev = sum(rev_tot)) %>%
   ungroup() %>%
   mutate(cost = (best_rev - rev) / best_rev) %>%
   ggplot(aes(x = R, y = cost, color = alpha, group = paste(alpha, theta), linetype = theta)) +
   geom_line(size = 1.5) +
   scale_y_continuous(labels = scales::percent,
                      limits = c(0, 1)) +
   xlab("Portion of patch as reserve (R)") +
   ylab("Costs\n(% of case with R = 0)") +
   scale_color_viridis_c() +
   scale_linetype_manual(values = c("solid", "dashed", "dotted")) +
   ggtheme_plot() +
   # facet_wrap(~trade, ncol = 1) +
   guides(color = guide_colorbar(title = quo("Allocation\nparameter ("~alpha~")"),
                                 ticks.colour = "black",
                                 frame.colour = "black"),
          linetype = guide_legend(title = quo("Movement\nparameter ("~theta~")"),
                                  override.aes = list(size = 0.5))))
```
